Asteroid shape reconstruction

### 2018-03-23 abstract.tex
Starting on extended abstract

>>>>

\begin{itemize}
    \item Spacecraft missions around asteroid require long periods of mapping
        \begin{itemize}
            \item Several months/years are spent in a quiescent state devoted solely to mapping the surface
            \item Depending on the mission this time spent mapping is unnecessary and resource limiting - such as impact mitigation misions
            \item The main goal of this mapping process is to generate an accurate shape model of the asteroid and measure the surface features.
            \item The current methods rely on sending all data to the ground in order to compute the shape. 
            \item Furthermore this limits the abiilty  of teh spacecraft to operate without  reliable Earth communications and support
        \end{itemize}
\end{itemize}
